---
title: "The BROSAlab3 Package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Lab_3_R_Package_Making}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  message = FALSE,
  warning = FALSE
)
```

```{r setup}
library(BROSAlab3)
```

# Introduction

---

This vignette describes the use of the BROSAlab3 package, and shows you how to apply the ggmytable function to your own data frames. The ggmytable function takes as arguments a data frame (df), two categorical variables ($x$ and $y$), and one numerical variable ($z$). The package also contains the "MTBE" and "DDT" data sets for practice and experimentation.

# Example: Looks Fishy

---

Let's begin with an example using the the "DDT" data; a data set containing  measurements of 144 fish caught on various rivers. 

```{r}
ggmytable(ddt, "RIVER", "SPECIES", "WEIGHT")
```

The function returns a summary which finds the total number and mean weight ($z$) of each fish species ($y$). Further, it produces bar-plots displaying the number of each species caught on each river ($x$).  

_Note_ the quotations around the three variable names when using the function.  











